% this works fine with \documentclass{article}, for example
\documentclass[12pt,]{isuthesis}

% http://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\begin{document}

% commenting out this line doesn't help...
\specialchapt{BIBLIOGRAPHY}

% if you remove the hypertargets, the line breaks are computed correctly
\hypertarget{ref-rgl}{}
Adler, D., Murdoch, D., \& others. (2016). \emph{Rgl: 3D visualization
using opengl}. Retrieved from
\url{https://CRAN.R-project.org/package=rgl}
\\
\hypertarget{ref-Ahlberg:1991}{}
Ahlberg, C., Williamson, C., \& Shneiderman, B. (1991). Dynamic queries
for information exploration: An implementation and evaluation. In
\emph{ACM chi '92 conference proceedings} (Vol. 21, pp. 619--626).
\\
\hypertarget{ref-flexdashboard}{}
Allaire, J. (2016). \emph{Flexdashboard: R markdown format for flexible
dashboards}. Retrieved from
\url{https://CRAN.R-project.org/package=flexdashboard}
\\
\hypertarget{ref-rmarkdown}{}
Allaire, J., Cheng, J., Xie, Y., McPherson, J., Chang, W., Allen, J.,
\ldots{} Hyndman, R. (2016). \emph{Rmarkdown: Dynamic documents for r}.
Retrieved from \url{https://CRAN.R-project.org/package=rmarkdown}
\\
\hypertarget{ref-patent}{}
Alt, A., \& White, M. S. (2008, September 11). Tracking an object with
multiple asynchronous cameras. patent. Retrieved from
\url{http://www.patentlens.net/patentlens/patent/US_7062320/}
\\
\hypertarget{ref-viewing-pipeline}{}
Andreas Buja, C. H., Daniel Asimov, \& McDonald, J. A. (1988). Elements
of a viewing pipeline for data analysis. In W. S. Cleveland \& M. E.
McGill (Eds.), \emph{Dynamic graphics for statistics}. Belmont,
California: Wadsworth, Inc.
\\
\hypertarget{ref-grand-tour}{}
Asimov, D. (1985). The grand tour: A tool for viewing multidimensional
data. \emph{SIAM J. Sci. Stat. Comput.}, \emph{6}(1), 128--143.
\url{https://doi.org/10.1137/0906011}
\\
\hypertarget{ref-colourpicker}{}
Attali, D. (2016). \emph{Colourpicker: A colour picker widget for shiny
apps, rstudio, r-markdown, and 'htmlwidgets'}. Retrieved from
\url{https://CRAN.R-project.org/package=colourpicker}
\\
\hypertarget{ref-gridExtra}{}
Auguie, B. (2016). \emph{GridExtra: Miscellaneous functions for ``grid'' graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
\\
\hypertarget{ref-magrittr}{}
Bache, S. M., \& Wickham, H. (2014). \emph{Magrittr: A forward-pipe operator for r}. Retrieved from \url{https://CRAN.R-project.org/package=magrittr}
\\
\hypertarget{ref-etl}{} 
Baumer, B., \& Sievert, C. (2016). \emph{Etl: Extract-transfer-load framework for medium data}. Retrieved from \url{http://github.com/beanumber/etl}
\\
\hypertarget{ref-bayes-js}{}
Bååth, R. (2016). An implementation of a small mcmc framework and some
likelihood functions for doing bayes stats in the browser.
https://github.com/rasmusab/bayes.js.
\\
\hypertarget{ref-S:1978}{}
Becker, R. A., \& Chambers, J. M. (1978). Design and implementation of
the 's' system for interactive data analysis. \emph{Proceedings of
COMPSAC}, 626--629.
\\
\hypertarget{ref-brushing-scatterplots}{}
Becker, R., \& Cleveland, W. (1987). Brushing scatterplots.
\emph{Technometrics}, \emph{29}(2), 127--142.
\\
\hypertarget{ref-Bischof}{}
Bischof, J. M., \& Airoldi, E. M. (2012). Summarizing topical content
with word frequency and exclusivity. In \emph{Icml}.
\\
\hypertarget{ref-Blei-2009}{}
Blei, D. M., \& Lafferty, J. (2009). Visualizing topics with multi-word
expressions. \emph{Arxiv}. Retrieved from
\url{https://arxiv.org/pdf/0907.1013.pdf}
\\
\hypertarget{ref-crowdsourcing-graphical-perception}{}
Bostock, J. H. A. M. (2010). Crowdsourcing graphical perception: Using
mechanical turk to assess visualization design. In \emph{ACM human
factors in computing systems (chi)} (pp. 203--212). Retrieved from
\url{http://vis.stanford.edu/papers/crowdsourcing-graphical-perception}
\\
\hypertarget{ref-d3}{}
Bostock, M., Oglevetsky, V., \& Heer, J. (2011). D3 data-driven
documents. \emph{IEEE Transactions on Visualization and Computer
Graphics}, \emph{17}(12), 2301--2309.
\\
\hypertarget{ref-gapminder}{}
Bryan, J. (2015). \emph{Gapminder: Data from gapminder}. Retrieved from
\url{https://CRAN.R-project.org/package=gapminder}
\\
\hypertarget{ref-Gretarsson}{}
Brynjar Gretarsson, S. B., John O'Donovan, \& Smyth, P. (2011).
TopicNets: Visual analysis of large text corpora with topic modeling. In
\emph{ACM transactions on intelligent systems and technology}.
\\
\hypertarget{ref-Buja:2009hp}{}
Buja, A., Cook, D., Hofmann, H., Lawrence, M., Lee, E.-K., Swayne, D.
F., \& Wickham, H. (2009). Statistical inference for exploratory data
analysis and model diagnostics. \emph{Philosophical Transactions of the
Royal Society A: Mathematical, Physical and Engineering Sciences},
\emph{367}(1906), 4361--4383.
\\
\hypertarget{ref-Buja:1991vh}{}
Buja, A., McDonald, J. A., Michalak, J., \& Stuetzle, W. (1991).
Interactive data visualization using focusing and linking. \emph{IEEE
Proceedings of Visualization}, 1--8.


\end{document}
